---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
``` {r}
rough<-read.csv("activity.csv")
library("dplyr")
daystep<-summarize(group_by(rough, date), s=sum(steps), m=mean(steps), j=median(steps))

```

## What is mean total number of steps taken per day?
``` {r}
hist(daystep$s)

```
```{r, echo=FALSE}
stepmean<-sprintf(mean(daystep$s, na.rm = TRUE), fmt='%#.2f')
stepmedian<-sprintf(median(daystep$s, na.rm = TRUE), fmt='%#.2f')
```
1. The mean of the total number of steps taken is `r stepmean`.  

2. The median of the total number of steps taken is `r stepmedian`.  

## What is the average daily activity pattern?
``` {r}
intstep<-summarize(group_by(rough, interval), ave=mean(steps, na.rm = TRUE))
plot(intstep, type='l')
```

## Imputing missing values
``` {r}
totnas<-sum(is.na(rough$steps))
## source: http://www.mail-archive.com/r-help@r-project.org/msg58289.html

library("plyr")
impute.mean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
impsteps<-ddply(rough, ~ interval, transform, steps = impute.mean(steps))
impsteps<-impsteps[order(impsteps$date), ]
detach("package:plyr", unload=TRUE)
smostep<-summarize(group_by(impsteps, interval), ave=mean(steps))
plot(smostep, type='l')
```

1. The total number of missing values in the dataset are `r totnas`.

``` {r}
daystep2<-summarize(group_by(impsteps, date), s=sum(steps), m=mean(steps), j=median(steps))
hist(daystep2$s)
```

## Are there differences in activity patterns between weekdays and weekends?
